Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-25 scnn.tex
writing data section

The simulations are created using the fast lightcone method described in \citep{sgier2018fastgeneration}.
However, we use only a single simulation box, as opposed to two used in \citep{sgier2018fastgeneration}, as we use source galaxies at lower redshift of $z=1$, instead of $z=1.5$.
As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
For each class, we generate 30 simulations.
In the experiment we use data on a parts of the sphere, and we check the performance as a function of the area used.
We also test the performance as a function of noise level of the pixels.

% sim1: planck
% omega_m=0.31, pk_norm=0.82, h=0.7

% sim2: alternative model
% omega_m=0.26, sigma_8=0.91, h=0.7

Our data comes from a simulation with software ??? using the following parameters ???.

As a pre-processing step, we first remove the mean of each sample and we apply a
spherical Gaussian smoothing kernel with a radius of $1$ arcmin.

We made 30 simulations for each class. Out of the 60 simulations, 20 are kept
for the test set. The training and validation set are created later on.

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/smooth_map_class_1.pdf}
\includegraphics[width=0.95\textwidth]{figures/smooth_map_class_2.pdf}
\caption{One sample of each class.}
\label{fig:map_sample}
\end{figure*}

>>>>

The simulations are created using the fast lightcone method described in \citep{sgier2018fastgeneration}.
However, we use only a single simulation box, as opposed to two used in that work, as we use source galaxies at lower redshift of $z=1$, instead of $z=1.5$.
As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
For each class, we generate 30 simulations.
In the experiment we use data on a parts of the sphere, and we check the performance as a function of the area used.
We also test the performance as a function of noise level of the pixels.

As a pre-processing step, we first remove the mean of each sample and we apply a spherical Gaussian smoothing kernel with a radius of $1$ arcmin.
Out of the 60 simulations, 20 are kept for the test set.
% The training and validation set are created later on.
Figure \ref{fig:map_sample} shows the full sky simulations and a zoom region for model 1 (top) and model 2 (bottom).
Initial conditions for these simulations were the same, so the differences in structures can only be attributed to different cosmological parameters used to evolve the particle distribution.

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/smooth_map_class_1.pdf}
\includegraphics[width=0.95\textwidth]{figures/smooth_map_class_2.pdf}
\caption{Example maps from two classes. Top: model 1 ($\Omega_m=0.31, \sigma_8=0.82$). Bottom: model 2 ($\Omega_m=0.26, \sigma_8=0.91$).
The initial conditions for these simulations were the same, so differences arise only due to different cosmological parameters.}
\label{fig:map_sample}
\end{figure*}
